\documentclass[11pt, a4paper]{article}

\def\ncourse {}
\def\nterm {Winter}
\def\nyear {2025}
\def\nnumber {}

\input{../header.tex}

\begin{document}
\newpage

\section{Metric Spaces}
\begin{exercise}
  Let $\R^n$ be the Euclidean space with the Euclidean metric.
  \begin{enumerate}
    \item[(1)] Show that any set in $\R^n$ is open if and only if it is a union
      of open balls.
    \item[(2)] Show that any set in $\R^n$ is open if and only if it is a
      countable union of open balls.
  \end{enumerate}
\end{exercise}
\begin{solution} \phantom{}
\begin{enumerate}
  \item[(1)] Suppose that $A \subset \R^n$ is a union of open balls, then
    since each open ball is an open set, and the set of open sets is closed
    under unions, the set $A$ is open.

    Next suppose that $A \subset \R^n$ is open.
    Since $A$ is open, for each $a \in A$ there exists $r_a$ such that
    \[
      (*)\,B(a,r_a) \subset A.
    \]
    Consider the set
    \[
      B := \bigcup_{a \in A} B(a,r_a).
    \]
    Let $a \in A$. Then there exists $B(a,r_a)$ such that 
    $a \in B(a,r_a) \subset B$.
    Then $a \in B$. Then there exists $B(a,r_a)$ such that 
    $a \in B(a,r_a) \underset{(*)}{\subset} A$.
    Therefore $A = B$ which means that $A$ is a union of open balls which
    completes the proof.
  \item[(2)] Let $A$ be a countable union of open balls.
    It is clear from $(1)$ that it is open.
    Next suppose that $A$ is open.
    Denote
    \[
      \mathcal Q := \set{x \in A \mid x \in \Q^n}
    \]
    We have that
    \[
      |\mathcal Q| \le |\Q^n| = \aleph_0
    \]
    so $\mathcal Q$ is countable.
    For each $x \in \mathcal Q$ denote
    \[
      \mathcal B_x := \set{B(x,q) \mid q \in \Q \stand B(x,q) \subset A}.
    \]
    It is clear that $\mathcal B_x$ is countable.
    Therefore
    \[
      B :=
      \bigcup_{\substack{x \in \mathcal Q \\ B(x,q) \in \mathcal B_x}} B(x,q)
    \]
    is a countable union of open balls.
    
    Let $x \in B$. Then there exists $x' \in \mathcal Q$ and 
    $B(x',q) \in B_{x'}$ such that $x \in B(x,q) \subset A$.
    Let $x \in A$. Since $A$ is open, there exists $\delta > 0$ such that 
    $B(x,\delta) \subset A$.
    Since $\Q^n$ is dense in $\R^n$ there exists $q \in \Q^n$ such that
    $d(q,x) < \delta / 2$, which implies that $q \in B(x,\delta / 2) \subset A$
    so we also have $q \in \mathcal Q$.
    Since $\Q$ is dense in $\R$ we can
    choose $d(x,q) < \epsilon < \delta / 2$ such that $\epsilon \in \Q$.
    We notice that $B(q,\epsilon) \subset B(x,\delta) \subset A$ and that
    $x \in B(q, \epsilon) \in B$.
    Therefore $A = B$ which implies that $A$ is a countable union of open balls 
    which completes the proof.
\end{enumerate}
\end{solution}


\end{document}
