\documentclass[11pt,a4paper]{article}
\usepackage{amssymb,amsfonts,amsmath,calc,tikz,pgfplots,geometry}
\usepackage{color}   %May be necessary if you want to color links
\usepackage{hyperref}
\usepackage{amsthm}
\usepackage{fancyhdr}
\pagestyle{fancy}
\usetikzlibrary{positioning}
\geometry{margin=1in}
\hypersetup{
    colorlinks=false, %set true if you want colored links
    linktoc=all,   %set to all if you want both sections and subsections linked
    linkcolor=black,  %choose some color if you want links to stand out
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]
\newtheorem{remark}{Remark}[section]
\newtheorem{example}{Example}[section]
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\DeclareMathOperator{\lcm}{lcm}
\DeclareMathOperator{\idealin}{\triangleleft}
\DeclareMathOperator{\im}{im}
\DeclareMathOperator{\Aut}{Aut}
\DeclareMathOperator{\End}{End}
\DeclareMathOperator{\Inn}{Inn}
\DeclareMathOperator{\Out}{Out}
\DeclareMathOperator{\Mat}{Mat}
\DeclareMathOperator{\std}{std}
\DeclareMathOperator{\Int}{Int}
\newcommand{\N}{\mathbb{N}}
\newcommand{\st}{\text{ s.t. }}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\Omicron}{O}
\newcommand{\ip}[2]{\langle #1, #2 \rangle}
\newcommand{\set}[2]{ \left\{ #1 \mid #2 \right\} }
\newcommand{\abs}[1]{\left\lvert #1\right\rvert}
\newcommand{\norm}[1]{\left\lVert #1\right\rVert}
\renewcommand{\tt}[1]{\textnormal{\textbf{(#1).}}} %tt=theorem title
\newcommand{\bigslant}[2]
{{\raisebox{.2em}{$#1$}\left/\raisebox{-.2em}{$#2$}\right.}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{Introduction to Metric and Topological Spaces}}
\author{heavily based on notes by Ariel Rapaport}
\date{}
\begin{document}
	\maketitle
	\newpage
	\section{Metric Spaces}
	First we will begin with metric spaces.
	\begin{definition}
	Let $X$ be a non-empty set. A metric on $X$ is a function 
	$d \colon X \times X \to [0,\infty]$ such that for all $x,y,z \in X$,
	\end{definition}
	\begin{enumerate}
	\item $d(x,y) = 0$ if and only if $x = y$;
	\item $d(x,y) = d(y,x)$ (symmetry);
	\item $d(x,z) \le d(x,y) + d(y,z)$ (triangle inequality);
	\end{enumerate}
	\emph{The pair $(X,d)$ is said to be a \textbf{metric space}.}
	\begin{example}
	Let $X$ be a non-empty set. Let $d \colon X \times X \to [0,\infty)$ be
	the function such that for $x,y \in X$,
	\[
		d(x,y) := \begin{cases}
			0, & x=y \\
			1, & x \neq y
		\end{cases}
	\]
	The function $d$ is a metric and it is called \textbf{the discrete metric}
	on $X$.
	\end{example}
	\begin{example}
	Let $X = \R^n$ and define the function:
	\[
		d(x-y) := |x - y|
	\]
	Where $|\cdot | \colon \R \to \R$ is the Eclidean norm function. 
	Then the pair $(X, d)$ forms a metric space.
	\end{example}
	\begin{example}
	Let $(X, N)$ be an arbitrary normed space and define the function:
	\[
		d(x-y) := N(x - y)
	\] 
	Then the pair $(X, d)$ forms a metric space.
	\end{example}
	\begin{example}
	The pair $(C([0,1]), d)$ such that $C([0,1])$ is the space of all
	continuous functions on $[0,1]$ paired with the metric:
	\[
		d(f,g) = \int_{0}^{1}{|f(x) - g(x)|\,dx}
	\]
	Is also a metric space.
	\end{example}
	\begin{example}
	The pair $(C([0,1]), d)$ paired with the supremum metric:
	\[
		d(f,g) = \sup_{x \in [0,1]}{|f(x) - g(x)|}
	\]
	Is also also metric space.
	\end{example}
	\begin{example}
	Let $\Lambda$ be a nonempty set which will represent an alphabet.
	The set $\Lambda^{\N}$ represents all the sequences over that alphabet.
	The pair $(\Lambda^\N, d)$ with the metric $d$ defined on two sequences
	$\omega = (\omega_n)_{n=1}^{\infty}, \eta = (\eta_n)_{n=1}^{\infty}$
	as:
	\[
		d(\omega, \eta) = \begin{cases}
			2^{-\min\{n \geq 0 \mid \omega_n \neq \eta_n\}} & 
			\omega \neq \eta \\
			0 & \omega = \eta
		\end{cases}
	\]
	\end{example}
	
	\newpage
	
	\section{Topological Spaces}
	\begin{definition}
		Let $X$ be a nonempty set. A collection $\tau \subset P(X)$ is said to
		be a topology on $X$ if it satisfies the following properties,
		\begin{enumerate}
			\item $X$, $\emptyset \in \tau$;
			\item Any union of sets in $\tau$ is a set in $\tau$;
			\item Any finite intersection of sets in $\tau$ is a set in $\tau$;
		\end{enumerate}
		The pair $(X,\tau)$ is said to be a topological space and $U \in \tau$
		an open set of $(X,\tau)$. An element $x \in X$ is said to be a point
		of $(X,\tau)$.
	\end{definition}
	\begin{example}
		Every metric spaces can induce a topological space. Let $(X,d)$ be a
		metric space. It can be verified that:
		\[
			\tau := \set{U \subset X}{\forall x \in U \quad \exists \epsilon > 0
			\st B(x,\epsilon) \subset U}
		\]
		Is a topology on $X$.
	\end{example}
	\begin{definition}
		We say that a topological space $(X,\tau)$ is metrizable if exists a 
		metric $d$ on $X$, such that the topology that $d$ induces on $X$
		is equal to $\tau$.
	\end{definition}
	\begin{example}
		Let $X$ be a nonempty set and let $\tau := P(X)$. The topology $\tau$
		is called the discrete topology and the space $(X,\tau)$ is called the 
		discrete space. Is it metrizable?
	\end{example}
	\begin{example}
		Let $X$ be a nonempty set and let $\tau := \{\emptyset,X\}$. The topology 
		$\tau$ is called the trivial topology. Is it metrizable when $|X| = 1$?
		Is it metrizable when $|X| > 1$?
	\end{example}
	\begin{example}
		Let $X$ be any infinite set and let 
		$\tau := \set{A \subset X}{\abs{X \setminus A} < \infty} \cup
		\{\emptyset\}.$ 
		The topology $\tau$ is called the finite complement topology. Is it 
		metrizable?
	\end{example}
	\begin{definition}
		A mapping $f \colon X \to Y$ is said to be continuous if for every open
		set $U \subset Y$ the set $f^{-1}(U)$ is open.
	\end{definition}
	\begin{definition}
		Given $x \in X$, an open $U \subset X$ containing $x$ is said to be a
		neighbourhood of $x$.
	\end{definition}
	\begin{definition}
		A mapping $f \colon X \to Y$ is said to be continuous at $x$ if for 
		every neighbourhood $U$ of $f(x)$ there exists a neighbourhood $V$
		of $x$ such that $f(V) \subset U$.
	\end{definition}
	\begin{definition}
		A mapping $f \colon X \to Y$ is said to be open if $f(U)$ is open in $Y$
		for every open $U \subset X$.
	\end{definition}
	\begin{definition}
		A mapping $f \colon X \to Y$ is said to be a homeomorphism if it is
		injective, surjective, continuous and open. If there exists such an $f$, 
		then we say that $X$ and $Y$ are homeomorphic.
	\end{definition}
	\begin{remark}
		We say that a property $P$ is a \emph{topological property} if for every
		two homeomorphic spaces $X$ and $Y$, then $P$ holds for $X$ if and only
		if it holds for $P$. The branch that deals with topological properties
		is called topology.
	\end{remark}
	\begin{definition}
		Let $(X,\tau_X)$ be a topological space and let $\emptyset \neq Y \subset 
		X$. Define
		\[
			\tau_Y = \set{U \cap Y}{U \in \tau_X}
		\]
		We call $\tau_Y$ the subspace topology, induced by $\tau_X$ on $Y$.
	\end{definition}
	\begin{proposition}
		\textnormal{\textbf{(Characteristic property of the subspace topology).}}
		Let $(X, \tau_X)$
		be a topological space, let $\emptyset \neq Y \subset X$, and write 
		$\tau_Y$ for the subspace topology on $Y$. Then $\tau_Y$ is the unique 
		topology on $Y$ which satisfies the following property. Let $Z$
		be a topological space and let $f \colon Z \to X$ be with 
		$f(Z) \subset Y$. Then $f$ is continuous as a map into $(X, \tau_X)$ if 
		and only if it is continuous as a map into $(Y, \tau_Y)$.
	\end{proposition}
	Throughout this section let $X$ be a fixed topological space.
	\begin{definition}
		A subset $F$ of $X$ is said to be closed if $F^c = X \setminus F$ is open.
	\end{definition}
	\begin{proposition}
		The following properties are always satisfied:
		\begin{enumerate}
			\item $X$, $\emptyset$ are closed;
			\item Any intersection of closed sets is closed;
			\item Any finite union of closed sets is closed;
		\end{enumerate}
	\end{proposition}
	\begin{definition}
		Given $A \subset X$ we denote $\overline{A}$ to be the intersection of
		all $F \subset X$ such that $A \subset F$ and $F$ is closed. We call
		$\overline{A}$ the closure of $A$.
	\end{definition}
	We can also define the closure of $A$ in an alternate way:
	\[
		\overline{A} = \set{x \in X}{A \cap U \neq \emptyset \,\,\text{for each 
		neighbourhood $U$ of $x$}}.
	\]
	You may try to prove that both definitions are equivalent.
	\begin{definition}
		A subset $A$ of $X$ is said to be dense in $X$ if $\overline{A} = X$.
	\end{definition}
	Note that the second definition of closure we get that $A$ is dense in $X$
	if and only if $A \cap U \neq \emptyset$ for every nonempty $U \subset X$.
	\begin{definition}
		We say that $X$ is seperable if it has a countable dense subset.
	\end{definition}
	\begin{definition}
		Let $A \subset X$. We say that $x$ is an isolated point of $A$ if exists
		$U$ open in $X$ such that $X \cap U = \{x\}$.
	\end{definition}
	This is exactly the same as saying that $x$ is an isolated point if and
	only if the singleton $\{x\}$ is open in the subspace topology.
	\begin{definition}
		Let $A \subset X$. We say that $x$ is a limit point of $A$ if for every
		neighourhood $U$ of $x$ there exists $a \in U \cap A$ with $a \neq x$.
		The set of all limit points of $A$ is called the derived set of $A$
		and is denoted by $D(A)$.
	\end{definition}
	\begin{proposition}
		Let $A \subset X$ be given, then
		\begin{enumerate}
			\item $\overline{A} = A \cup D(A)$.
			\item $A$ is closed if and only if $D(A) \subset A$.
		\end{enumerate}
	\end{proposition}
	\begin{corollary}
		Let $A \subset X$ be closed and write $I(A)$ for the set of all isolated
		points of $A$. Then $A$ is the disjoint union of $D(A)$ and $I(A)$.
	\end{corollary}
	\begin{definition}
		Let $A$ be a subset of $X$. The interior of $A$ is denoted by $\Int(A)$
		and is defined to be the union of all open subsets $U$ of $X$ so that 
		$U \subset A$. A point $x \in \Int(A)$ is said to be an interior point 
		of $A$.
	\end{definition}
	\begin{proposition}
		Let $A \subset X$ be given, then
		\begin{enumerate}
			\item $\Int{A} = X \setminus \overline{(X \setminus A)}$.
			\item $\Int(A)$ is open and contained in $A$.
			\item $A$ is open if and only if $A = \Int(A)$.
		\end{enumerate}
	\end{proposition}
	\begin{definition}
		Let $A \subset X$ be given. A point $x \in X$ is said to be a boundary
		point of $A$ if for every neighbourhood $U$ of $x$ we have 
		$U \cap A \neq \emptyset$ and $U \cap (X \setminus A) \neq \emptyset$.
		The set of all boundary points of $A$ is called the boundary of $A$ and 
		is denoted by $\partial A$.
	\end{definition}
	\begin{proposition}
		For $A \subset X$ we have 
		$\partial A = \overline{A} \cap \overline{X \setminus A}$ and in 
		particular $\partial A$ is closed.
	\end{proposition}
	\begin{proposition}
		Let $A \subset X$ be given, then $A$ is the disjoint union of $\Int(A)$
		and $\partial A$.
	\end{proposition}
	\begin{definition}
		A family $\mathcal{B}$ of subsets of $X$ is said to be an open base
		for $X$ if for each open $U \subset X$ and $x \in U$ exists 
		$B \in \mathcal{B}$ such that $x \in B \subset U$.
	\end{definition}
	It is easy to see that a family $\mathcal{B}$ of open subsets of $X$ is an 
	open base for $X$ if and only if each open $U \subset X$ is a union of 
	elements of $\mathcal{B}$.
	\begin{definition}
		We say that $X$ is second countable, or that it satisfies the second
		axiom of countability, if it has a countable open base.
	\end{definition}
	\begin{proposition}
		Suppose that $X$ is second countable, then $X$ is separable.
	\end{proposition}
	\begin{proof}
		Let $\mathcal{B}$ be a countable open base for $X$. We have that 
		$\mathcal{B} \setminus \{\emptyset\}$ is also an open base. Choose
		an arbitrary $x_B \in B$ for each $B \in \mathcal{B}$. Since 
		$\mathcal{B}$ is countable $\{x_B\}_{B \in \mathcal{B}}$ is also 
		countable. Let $U$ be open in $X$. By defintion of an open base exists 
		$B \in \mathcal{B}$ such that $x_B \in B$ and $B \subset U$ so 
		$x_B \in U$. This shows that $\{x_B\}_{B \in \mathcal{B}}$ is dense
		in $X$ and thus $X$ is seperable.
	\end{proof}
	\begin{remark}
		In metric spaces, the property of being seperable and second countable
		is equivalent. If we denote $(X,d)$ the metric space and $A$ the 
		countable dense set, then
		\[
			\mathcal{B} = \set{B(a,q)}{a \in A \text{ and } q \in \Q \cap 
			(0,\infty)}
		\]
		Will form a countable open base for $X$.
	\end{remark}
	\begin{example}
		A classic example of a topological space that is seperable but not
		second countable is the Sorgenfrey line, also known as the lower
		limit topology, which we will discuss later.
	\end{example}
	\begin{theorem}
		\tt{Lindelöf’s Theorem} Suppose that $X$ is second countable. Let
		$\{U_i\}_{i \in I}$ be a family of open subsets of $X$. Then there
		exists a countable $I_0 \subset I$ so that 
		$\cup_{i \in I_{0}}{U_i} = \cup_{i \in I}{U_i}$
	\end{theorem}
	\begin{proof}
		
	\end{proof}
	
	
	
	\newpage
	
	\section{Compactness}
	Let $X$ be a fixed topological space.
	\begin{definition}
		A class $\mathcal{U} := \{U_i\}_{i \in I}$ of open subsets of a
		$X$ is said to be an \emph{open cover of $X$} if 
		$X = \bigcup_{i \in I} U_i$. A subclass of $\mathcal{U}$ is said
		to be a subcover of $\mathcal{U}$ if it is in itself an open cover
		of $X$.
	\end{definition}
	\begin{definition}
		The space $X$ is said to be compact if every open cover of $X$
		has a finite subcover.
	\end{definition}
	\begin{definition}
		A subset $Y$ of $X$ is said to be compact if for every family of open
		sets $\{U_i\}_{i \in I}$ such that $Y \subset \bigcup_{i \in I} U_i$
		exists a finite index set $I_0 \subset I$ such that 
		$Y \subset \bigcup_{i \in I_0} U_i$.
	\end{definition}
	\begin{remark}
		It follows easily from the definition of the subspace topology that 
		a nonempty subset $Y$ of $X$ is compact if and only if $Y$ is a 
		compact space when equipped with the subspace topology.
	\end{remark}
	\begin{proposition}
		Suppose that $X$ is compact and let $F \subset X$ be closed. Then
		$F$ is compact.
	\end{proposition}
	\begin{proof}
		Let $\{U_i\}_{i \in I}$ be an open cover of $F$. Since $F$ is closed
		we know that $X \setminus F \cup \{U_i\}_{i \in I}$ is an open cover
		of $X$. Since $X$ is compact exists a finite index set $I_0 \subset I$
		such that $X \setminus F \cup \{U_i\}_{i \in I_0}$ is a finite
		open cover of $X$. It is clear that $F \subset \{U_i\}_{i \in I_0}$
		which completes the proof.
	\end{proof}
	\begin{proposition}
		Suppose $X$ is compact, let $Y$ be a topological space, and let
		$f \colon X \to Y$ be continuous. Then $f(X)$ is compact.
	\end{proposition}
	\begin{proof}
		Let $\{U_i\}_{i \in I}$ be an open cover of $f(X)$. Since $f$
		is continuous $\{f^{-1}(U_i)\}_{i \in I}$ is an open cover of $X$.
		Since $X$ is compact exists a finite index set $I_0 \subset I$
		such that $\{f^{-1}(U_i)\}_{i \in I_0}$ is an open cover of $X$.
		We now have:
		\[
			f(X) = f(\cup_{i \in I_0} f^{-1}(U_i)) = 
			\cup_{i \in I_0} f(f^{-1}(U_i)) = 
			\cup_{i \in I_0} U_i
		\]
		Which completes the proof.
	\end{proof}
	Here are some more equivalent forms of compactness that are ofter easier
	to apply.
	\begin{proposition}
		The space $X$ is compact if and only if for every class 
		$\{F_i\}_{i \in I}$ of closed subsets of $X$ with 
		$\cap_{i \in I}{F_i} = \emptyset$ there exists a finite 
		$I_0 \subset I$ with $\cap_{i \in I_0} {F_i} = \emptyset.$
	\end{proposition}
	\begin{proof}
		Assume $X$ is compact. Let $\{F_i\}_{i \in I}$ be a family of closed 
		subsets of $X$ with $\cap_{i \in I}{F_i} = \emptyset$ then 
		we have
		$\cap_{i \in I} {X \setminus F_i} = X$ which is a cover of $X$
		thus exists a finite $I_0 \subset I$ with 
		$\cap_{i \in I_0} {X \setminus F_i} = X$ being a finite subcover
		of $X$. This implies that $\cap_{i \in I_0} {F_i} = \emptyset$
		which completes the proof. The proof of the other direction is
		similar and thus omitted. 
	\end{proof}
	\begin{definition}
		Let $S$ be a nonempty set. A class of subsets $\{E_i\}_{i \in I}$ of 
		$S$ is said to have the \textbf{finite intersection property} if 
		$\cap_{i \in I_0}{E_i} \neq \emptyset$ for every finite 
		$I_0 \subset I$.
	\end{definition}
	\begin{proposition}
		The space $X$ is compact if and only if every class of closed
		subsets of $X$ with the finite intersection property has nonempty 
		intersection.
	\end{proposition}
	\begin{proposition}
		Let $B$ be an open base for $X$. Suppose that every open cover
		$\{B_i\}_{i \in I} \subset B$ of $X$ has a finite subcover. Then $X$ 
		is compact.
	\end{proposition}
	\begin{definition}
		A family $\mathcal{B}$ of closed subsets of $X$ is called a 
		\textbf{closed base} for $X$ if the collection
		\[
			\{X \setminus B \colon B \in \mathcal{B}\}
		\]
		is an open base for $X$. Similarly, a family $\mathcal{S}$ of
		closed subsets of $X$ is called a \textbf{closed subbase} for $X$ 
		if the collection $\{X \setminus S \colon S \in \mathcal{S}\}$ is 
		an open subbase for $X$.
	\end{definition}
	\begin{remark}
		Note that if $\mathcal{S}$ is a closed subbase for $X$ then the set 
		$\mathcal{B}$ of all finite unions of elements of $\mathcal{S}$ forms 
		a closed base for $X$. This is so since, by definition,
		the set of all finite intersections of an open subbase forms an open 
		base. We call $\mathcal{B}$ the closed base generated by 
		$\mathcal{S}$.
	\end{remark}
	\begin{proposition}
		Let $\mathcal{B}$ be a closed base for $X$. Suppose that for every 
		$\{B_i\}_{i \in I} \subset \mathcal{B}$ with the finite intersection 
		property we have $\cap_{i \in I}{B_i} = \emptyset$. Then $X$ is 
		compact.
	\end{proposition}
	
	\newpage
	
	\section{The Alexander Subbase Theorem}
	\begin{theorem}
		Let $\mathcal{S}$ be an open subbase for $X$. Suppose that every 
		open cover $\{S_i\}_{i \in I} \subset \mathcal{S}$ of $X$ has a 
		finite subcover. Then $X$ is compact.
	\end{theorem}
	The thoerem also has a second form:
	\begin{theorem}
	Let $\mathcal{S}$ be a closed subbase for $X$. Suppose that 
	$\cap_{i \in I}{S_i} = \emptyset$ for every 
	$\{S_i\}{i \in I} \subset \mathcal{S}$ with the finite intersection 
	property. Then $X$ is compact.
	\end{theorem}
	The proof of this theorem is concerned with Zorn's lemma and will
	be omitted for now.
	
	\newpage
	
	\section{Boundedness}
	\begin{definition}
		Let $X$ be a metric space. We say that $A \subset X$ is 
		\textbf{bounded} if exists $r > 0$ and $x \in X$ such that
		$A \subset B(x,r)$.
	\end{definition}
	Note that it is easy to see that $A \subset X$ is bounded if and only
	if it has a finite diameter.
	\begin{lemma}
		Let $\mathcal{S}$ be an open subbase for a topological space $X$.
		If $Y \subset X$ is a subset of $X$ equiped with the subspace
		topology induced by $X$ then $\{S \cap Y \mid S \in \mathcal{S}\}$
		is an open subbase for $Y$.
	\end{lemma}
	\begin{proof}
		Let $U$ be a nonempty subset of $Y$ and let $y \in U$. There
		exists $W$ an open set in $X$ such that $W \cap Y = U$. Because
		$\mathcal{S}$ is a subbase for $X$ exists 
		$S_1,\dots,S_n \in \mathcal{S}$ such that 
		$y \in \cap_{i=1}^{n}{S_i} \subset W$ and thus because $y \in Y$:
		\[
			y \in \cap_{i=1}^{n}{S_i \cap Y} \subset W \cap Y = U
		\]
		Because $S_i \cap Y$ are all open in $Y$ we have that indeed
		$\{S \cap Y \mid S \in \mathcal{S}\}$ is an open subbase as wanted.
	\end{proof}
	We will now prove the Heine-Borel theorem in $\R$.
	\begin{theorem}
		Every closed and bounded set in $\R$ is compact.
	\end{theorem}
	\begin{proof}
		Let $A$ be a closed and bounded set in $\R$. Because $A$ is bounded
		we know that exist real numbers $a,b \in \R$ such that $a < b$ and
		also $A \subset [a,b]$. If we equip $[a,b]$ with the subspace
		topology induced on it by $\R$ it is not hard to see that $A$ is
		closed in $[a,b]$ and thus it suffices to verify that $[a,b]$
		is compact in $\R$. It's easy to check that the set:
		\[
			\{(-\infty, c) \mid c \in \R\} \cup 
			\{(d, \infty) \mid d \in \R\}
		\]
		Is an open subbase to $\R$. From the lemma we have that the set:
		\[
			S = \{[a, c) \mid a < c \le b\} \cup 
			\{(d, b] \mid a < d \le b\}
		\]
		Is an open subbase for $[a,b]$. Let $\mathcal{U} \subset S$ be an
		open cover of $[a,b]$, by Alexander's subbase theorem it suffices
		to show that $\mathcal{S}$ has a finite subcover. Since 
		$\mathcal{U} \subset \mathcal{S}$ there exist index sets $I,J$ such 
		that:
		\[
			\mathcal{U} = 
			\{[a,c_i) \mid i \in I\} \cup \{(d_j,b] \mid j \in J\}
		\]
		We have that $a \in [a,b]$ and $\mathcal{U}$ a cover of $[a,b]$
		which means that $I \neq \emptyset$. 
		Denote $s = \sup\{c_i\}_{i\in I}$,  if we have $s \le d_j$ for
		all $j \in J$ we have $s \notin \cup\mathcal{U}$ which is a 
		contradiction. Otherwise exists $j_0 \in J$ such that 
		$d_{j_0} < s$ and then by definition exists $i_0 \in I$ such that
		$d_{j_0} < c_{i_0} < s$ and then we have that 
		$\{[a,c_{i_0}), (d_{j_0},b]\}$ is a finite subcover of $[a,b]$ which
		completes the proof.
	\end{proof}
	
	\newpage
	
	\section{Tychonoff’s theorem}
	\begin{theorem}
		Let $\{X_i\}_{i \in I}$ be a nonempty family of compact topological 
		spaces. Equip $\prod_{i \in I}{X_i}$ with the product topology. Then 
		$\prod_{i \in I}{X_i}$ is compact.
	\end{theorem}
	\begin{proof}
		Set:
		\[
			\mathcal{S} = 
			\left\{\prod_{i \in I}{F_i} \mid \exists i_0 \in I \st
			(\forall i \in I \setminus \{i_0\})(F_i = X_i) \land
			F_{i_0} \text{ is closed in } X_{i_0}
			\right\}
		\]
		This is the standard closed subbase for $\prod_{i \in I}{X_i}$.
		Let $\{S_j\}_{j \in J} \subset \mathcal{S}$ be with the finite
		intersection property. By Alexander's subbase theorem it suffices
		to prove that $\cap_{j \in J}\{S_j\} \neq \emptyset$ to conclude
		that $\prod_{i \in I}{X_i}$ is compact.
		NOT COMPLETED
	\end{proof}
	We can now prove a couple lemmas and then show that the Heine-Borel
	theorem is applicable on $\R^d$ as well for $d \in \N$.
	\begin{definition}
		A topological space $X$ is called \textbf{locally compact} if for
		any $x \in X$ exists a neighbourhood $U \subset X$ of $x$ so that
		$\overline{U}$ is compact.
	\end{definition}
	As an immediate result we get that for each $d \geq 1$ that $\R^d$
	is locally compact.
	\begin{definition}
		The metric space $X$ is said to be \textbf{sequentially compact} 
		if every sequence in $X$ has a convergent subsequence.
	\end{definition}
	\begin{definition}
		The metric space $X$ is said to have the 
		\textbf{Bolzano–Weierstrass property} if every infinite subset of 
		$X$ has a limit point in $X$.
	\end{definition}
	It is important to note that in metric spaces, sequential compactness and 
	the Bolzano–Weierstrass property are both
	equivalent to compactness. We will omit the proofs because there's not
	enough time. Here are some more definitions without
	motivation, and a lemma without a proof.
	\begin{definition}
		Let $\{U_i\}_{i \in I}$ be an open cover of $X$. A real number 
		$\delta > 0$ is said to be a \textbf{Lebesgue number} 
		for $\{U_i\}_{i \in I}$
		if for all nonempty $A \subset X$ with $\text{diam}(A) < \delta$
		there exists $i \in I$ so that $A \subset U_i$.
	\end{definition}
	\begin{lemma}
		(Lebesgue’s covering lemma). Suppose that $X$ is sequentially 
		compact. Let $\{U_i\}_{i \in I}$ be an open cover of $X$. 
		Then $\{U_i\}_{i \in I}$ has a Lebesgue number.
	\end{lemma}
	\begin{definition}
		Let $\epsilon > 0$ be given. A nonempty subset $A$ of $X$ is 
		said to be an \textbf{$\epsilon$-net} if $A$ is finite and 
		$X = \cup_{a \in A}{B(a, \epsilon)}$.
	\end{definition}
	\begin{definition}
		We say that $X$ is \textbf{totally bounded} if it has an 
		$\epsilon$-net for all $\epsilon > 0$.
	\end{definition}
	It is clear that a totally bounded space is also bounded. 
	Using Lebesgue's lemma we can also prove the following proposition:
	\begin{proposition}
		Suppose that a metric space $X$ is compact. Let $(Y, d_Y)$ be a 
		metric space, and let $f \colon X \to Y$ be continuous. Then $f$ is 
		uniformly continuous.	
	\end{proposition}
	\begin{proof}
		Let $\epsilon > 0$. Since $f$ is continuous the set 
		$f^{-1}(B(f(x),\epsilon/2))$ is open for any $x \in X$ and thus
		the set:
		\[
			\mathcal{U} := \{f^{-1}(B(f(x),\epsilon/2))\}_{x \in X}
		\]
		Is an open cover for $X$. Because $X$ is a compact metric space
		it is also sequencially compact, and thus from Lebesgue's lemma
		we have that exists a Lebesgue number $\rho > 0$ for $\mathcal{U}$.
		Now let $x_1,x_2 \in X$ such that $d(x_1,x_2) < \rho$, by definition
		exists $x \in X$ such that $x_1,x_2 \in f^{-1}(B(f(x),\epsilon/2))$,
		thus:
		\[
			d_Y(f(x_1),f(x_2)) \le d_Y(f(x_1),f(x)) + d_Y(f(x),f(x_2)) <
			\frac{\epsilon}{2} + \frac{\epsilon}{2} = \epsilon
		\]
	\end{proof}
	There is also a connection between compactness and total boundness as
	we see in the following proposition.
	\begin{proposition}
		The metric space $X$ is compact if and only if it is complete
		and totally bounded.
	\end{proposition}
	The proof will be omitted for now.
	\begin{corollary}
		Suppose that $X$ is complete and let $A$ be a nonempty closed subset
		of $X$. Then $A$ is compact if and only if it is totally bounded.
	\end{corollary}
	
	\newpage
	
	\section{The Arzelà–Ascoli theorem}
	First we define a new structure. Let $K$ be a field and $A$ a vector 
	space. Let $|\cdot| \colon A \times A \to A$ be a binary operation.
	Then $A$ is called an \textbf{algebra} if for each $x,y,z \in V$ 
	the following identites hold:
	\begin{itemize}
		\item Left distributiviy: $(x + y) \cdot z = x \cdot z + y \cdot z$.
		\item Right distributiviy: $z \cdot (x + y) = z \cdot x + z \cdot y$.
		\item Compatibility with scalars: 
		$(ax) \cdot (by) = (ab) (x \cdot y)$.
	\end{itemize}
	These identites actually just imply that the operation is bilinear.
	An algebra over $K$ is sometimes called a $K$-algebra and $K$ is
	called the base field of $A$. Notice that we didn't require the operation
	to be associative or commutative, although some authors use the term
	``algebra'' to refer to an associative algebra.
	\begin{definition}
		Given $K$-algebras $A$, $B$ then a homomorphism of $K$-algebras
		is a $K$-linear map $f \colon A \to B$ such that $f(xy)=f(x)f(y)$
		for all $x,y \in A$. If $A$ and $B$ are unital then the morphism
		$f(1_A) = 1_B$ is called the unital homomorphism. The space
		of all $K$-algebra homomorphisms between $A$ and $B$ is usually 
		written as ${\mathrm{Hom}}_{K\text{-alg}}(A,B)$. A $K$-algebra
		isomorphism is a bijective $K$-algebra homomorphism.
	\end{definition}
	A subalgebra of a $K$-algebra $A$ is a linear subspace of $A$ such
	that all products and sums of the subspace are themselves elements
	of the subspace. For examples $\R$ with complex addition and 
	multiplication as a subspace of the $\R$-algebra $\C$ is an example
	of a subalgebra.
	
	Similarly to rings, algebras also have a concept of ideals. A left ideal
	$L$ of a $K$-algebra $A$, is a linear subspace of $A$ such that for
	any $x,y \in L$, $c \in K$, $z \in A$ the following three identities
	are satisfied:
	\begin{itemize}
		\item $L$ is closed under addition: $x + y \in L$
		\item $L$ is closed under scalar multiplication: $cx \in L$
		\item $L$ is closed under vector multiplication from the left
		by arbitrary elements: $z \cdot x \in L$
	\end{itemize}
	We can similarly define a right ideal. An ideal that is both a left and
	a right ideal is called a two-sided ideal or simply an ideal. Notice
	that every ideal is a subalgebra and that in a commutative algebra
	any ideal is a two-sided ideal. Also notice that in contrast to an
	ideal of rings, here we also have a the requirement for closure under
	scalar multiplication and not just being a subgroup of addition.
	If the algebra is unital then the third requirement implies the second
	one.
	
	You can also talk about extension of scalars but I don't know what
	that is yet.
	
	Let $(X,d)$ be a fixed compact metric space. Denote $C(X)$ the algebra
	of all continuous functions $f \colon X \to \R$ and $C_b(X)$ the
	subalgebra of all the boundded functions in $C(X)$. Because $X$
	is compact we know that the image $f(X)$ of any $f \in C(X)$ is compact
	and in particular bounded and thus $C_b(X) = C(X)$. This means we can set 
	the norm $|\cdot|_\infty$ on $C(X)$. We can thus consider $C(X)$ as
	a metric space with the metric induced on it by $|\cdot|_\infty$.
	We will soon establish a useful characterisation of the compact sets
	in $C(X)$.
	\begin{definition}
		A subset $F \subset C(X)$ is called \textbf{equicontinuous} if
		for any $\varepsilon > 0$ exists a $\delta > 0$ such that
		$\abs{f(x) - f(y)} < \varepsilon$ for any $f \in F$ and $x,y \in X$ with
		$d(x,y) < \delta$.
	\end{definition}
	\begin{theorem}
		\tt{Arzelà–Ascoli theorem} Let $F$ be a nonempty closed subset of 
		$C(X)$. Then $F$ is compact if and only if it is bounded and 
		equicontinuous.
	\end{theorem}
	\begin{remark}
		It is easy to see that $F$ is bounded if and only if there exists 
		$M > 1$ so that $|f (x)| \le M$ for all $f \in F$ and $x \in X$.
	\end{remark}
	 
	\newpage
	
	\section{Seperation}
	Let $X$ be a fixed topological space.
	\begin{definition}
		We say that $X$ is a $T_1$\textbf{-space} if and only if for every
		$x_1, x_2 \in X$ exist neighbourhoods $U_1$ of $x_1$ and $U_2$ of
		$x_2$ such that $x_1 \notin U_2$ and $x_2 \notin U_1$.
	\end{definition}
	We can also verify that if $X$ is a $T_1$-space then every topological
	subspace of $X$ is also a $T_1$-space.
	\begin{proposition}
		The space $X$ is a $T_1$\textbf{-space} if and only if $\{x\}$ is 
		closed in $X$ for every $x \in X$.
	\end{proposition}
	\begin{proof}
		Suppose that $X$ is a $T_1$-space. Let $x \in X$. For every 
		$y \in X \setminus \{x\}$ exists a neighbourhood 
		$U_y \subset X \setminus \{x\}$ the union of which gives 
		$X \setminus \{x\}$ and then $\{x\}$ is closed as wanted. Now
		assume that $\{x\}$ is closed for every $x \in X$. For two points
		$x_1,x_2 \in X$ the sets $\{x_1\},\{x_2\}$ are closed and thus
		we have $U_1 := X \setminus \{x_1\}$ neighbourhood of $x_1$ and
		$U_2 := X \setminus \{x_2\}$ neighbourhood of $x_2$ such that
		$x_1 \notin U_2$ and $x_2 \notin U_1$.
	\end{proof}
	\begin{definition}
		We say that $X$ is a \textbf{Hausdorff space} if for all distinct 
		$x_1, x_2 \in X$ there exist open sets $U1, U2 \subset X$ with 
		$x_1 \in U_1, x_2 \in U_2$ and $U_1 \cap U_2 = \emptyset$.
	\end{definition}
	We can verify that every Hausdorff space is a $T_1$-space and that if
	$X$ if a Hausdorff is a topological space then every subspace of $X$
	is also a Hausdorff space.
	\begin{proposition}
		Let $\{X_i\}_{i \in I}$ be a nonempty family of Hausdorff spaces. 
		Then the product space $\prod_{i \in I}{X_i}$ is also a Hausdorff 
		space.
	\end{proposition}
	\begin{proof}
		Let $\{x_i\}_{i \in I}, \{y_i\}_{i \in I}$ be distinct points
		in $\prod_{i \in I}{X_i}$. Therefore exists $i_0 \in I$ such that
		$x_{i_0} \neq y_{i_0}$. Because $X_{i_0}$ is a Hausdorff space 
		there exist open sets $U_x, U_y \subset X_{i_0}$ with 
		$x \in U_x, y \in U_y$ and $U_x \cap U_y = \emptyset$. We know that
		the projection $\pi_{i_0} \colon \prod_{i \in I}{X_i} \to X_{i_0}$
		is continuous and thus $\pi_{i_0}^{-1}(U_x)$ and $\pi_{i_0}^{-1}(U_y)$
		are two open and disjoint sets of $\prod_{i \in I}{X_i}$ such
		that $\{x_i\}_{i \in I} \in \pi_{i_0}^{-1}(U_x)$ and 
		$\{y_i\}_{i \in I} \in \pi_{i_0}^{-1}(U_y)$ as wanted. This shows
		that $\prod_{i \in I}{X_i}$ is a Hausdorff space which completes
		the proof.
	\end{proof}
	The following proposition is one of the most important properties of
	Hausdorff spaces.
	\begin{proposition}
		Suppose that $X$ is a Hausdorff space. Let $K$ be a compact subset
		of $X$ with $K \neq X$, and let $x \in X \setminus K$. Then there 	
		exist open sets $U, V \subset X$ so that $x \in U , K \subset V$ 
		and $U \cap V = \emptyset$.
	\end{proposition}
	\begin{proof}
		First we may suppose that $K \neq \emptyset$ otherwise we could
		choose $U = X$ and $V = \emptyset$. Since $X$ is Hausdorff for
		every $y \in K$ exist $U_y, V_y \subset X$ disjoint open sets 
		such that $x \in U_y$ and $y \in V_y$. We have 
		$K \subset \cup_{y \in Y}{V_y}$ but since $K$ is compact exist
		$y_1,\dots,y_n$ such that $K \subset \cup_{i=1}^{n}{V_{y_i}}$.
		We now define:
		\begin{align*}
			&V := \cup_{i=1}^{n}{V_{y_i}} \\
			&U := \cap_{i=1}^{n}{U_{y_i}}
		\end{align*}
		It is clear that both sets are open, and that $x \in U$ and
		$K \subset V$ and for every $i \in [n]$ we also see that:
		\[
			Y_{y_i} \cap U \subset V_{y_i} \cap U_{y_i} = \emptyset
		\]
		Which means that $U \cap V = \emptyset$ as wanted which completes
		the proof.
	\end{proof}
	\begin{corollary}
		Suppose that $X$ is a Hausdorff space. Then every compact subset
		of $X$ is closed.
	\end{corollary}
	\begin{proof}
		Let $K \subset X$ be compact. We may clearly assume that 
		$K \neq X$. Given $x \in X \subset K$, it follows from the previous
		proposition that there exists a neighbourhood $U$ of $x$ which is 
		contained in $X \setminus K$. This shows that $X \setminus K$ is a 
		union of open sets, and so it is itself open. Thus $K$ is 
		closed, which completes the proof. 
	\end{proof}
	One particularly useful result of this corollary is the following
	proposition:
	\begin{proposition}
		Suppose that $X$ is a Hausdorff space, let $Y$ be a compact 
		topological space, and let $f \colon Y \to X$ be a continuous 
		bijection. Then $f$ is a homeomorphism.
	\end{proposition}
	\begin{proof}
		All that's left to show is that $f$ is an open map. Let $U \subset Y$
		be open. It follows that $Y \setminus U$ is closed in a compact space
		and thus compact. Since $f$ is continuous $f(Y \setminus U)$ is
		compact. From the previous corollary $f(Y \setminus U)$ is closed.
		Since $f$ is a bijection we also have 
		$f(Y \setminus U) = X \setminus f(U)$. This implies that $U$ is open,
		so $f$ is an open map and the proof is complete.
	\end{proof}
	
	\newpage
	
	\section{Completely regular spaces and normal spaces.}
	\begin{definition}
		We say that $C_b(X)$ separates points if for every distinct 
		$x, y \in X$ there exists $f \in C_b(X)$ with $f(x) \neq f(y)$.
	\end{definition}
	
	
	
	
	
\end{document}